\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{lmodern}

\longindentation=0pt    
\signature{
  \begin{minipage}[t]{0.75\textwidth}
  Tianfang Zhang, PhD\\
  Former Researcher, RaySearch Laboratories
  \end{minipage}
}
\address{Stockholm, Sweden \\ \texttt{tianfang@kth.se}}
\date{\today}

\begin{document}

\begin{letter}{}

\opening{Dear Members of the PhD Admissions Committee,}

I am pleased to write this letter in support of Ivar Cashin Eriksson's application to your PhD program at the University of Copenhagen. I supervised Ivar during his Master's thesis at RaySearch Laboratories, where we collaborated on a project involving machine learning methods for cancer radiotherapy planning.

During our time working together, Ivar consistently demonstrated strong initiative and independence in driving the project forward. He approached complex technical challenges with curiosity and confidence, particularly in the areas of probabilistic modelling, medical image analysis, and optimization algorithms. His mathematical background enabled him to quickly grasp and apply advanced concepts.

Beyond his technical strengths, Ivar is sociable, friendly, and an excellent communicator. He was able to present his work clearly and effectively, both within our team and to external collaborators, making complex topics accessible without oversimplifying them. His positive attitude and professionalism made him a highly valued colleague.

I am confident that Ivar will thrive in a research setting and make meaningful contributions to your program. Please do not hesitate to reach out if you would like further details.

\closing{Sincerely,}

\end{letter}

\end{document}
